---
title: "Learning Collaborative Report: December 2024"
date: now
date-format: long
title-block-banner: true
format: docx
execute:
    echo: false
project: 
    output-dir: Outputs
    execute-dir: file
editor_options: 
  chunk_output_type: inline
---

```{r setup, include=FALSE}
library(readxl)
library(tidyverse)
library(readr)
library(lubridate, warn.conflicts = FALSE)
library(ggplot2)
library(RColorBrewer)
library(ggrepel)
library(fmsb)
library(ggplotify)
library(patchwork)
library(waffle)
library(terra)
library(tidyterra)
require(showtext)
require(ggtext)
library(patchwork)
library(cowplot) 

# https://quarto.org/docs/reference/formats/pdf.html

knitr::opts_knit$set(root.dir = "Z:/PI Folder/Srihari, Vinod/Projects, AS/Quarterly report/LC report repo-main")
```

```{r}
#| warning: false
#| message: false

temp <- read_excel("Data/LHN & STEP - PhoneScreen and CONSORT Data V2.xlsx", skip = 1)  
temp[] <- lapply(temp, function(x) {
  if (is.character(x) || is.factor(x)) {    x[x == "NA"] <- NA    }
  return(x)
})

# calls script that has all the assigned objects for the text
source("Code/01_NumbersForInTextReport.r")

```

## Inquiries made to the Learning Collaborative

The total number of inquiries made since the Learning Collaborative (LC) launch is **`r tot_inq`** (see @tbl-inquiry1 and @fig-inquiry2). Of these inquiries, `r LC_line` calls were made via the LC direct line, and `r Other_line` via other routes. Additionally, we have introduced two new categories, Quiz and Online Inquiry, to improve the classification of incoming inquiries.
Between Q~1~ (2024-01-31 \~ 2024-05-01) and Q~2~ (2024-05-01 \~ 2024-08-01), the percentage change in inquiry numbers is **`r percentageChange1`%**. Between Q~2~ and Q~3~ (2024-08-01 \~ 2024-11-01), the percentage change in inquiry numbers is **`r percentageChange2`%**. Between the end of Q~3~ and now, the percentage change in inquiry numbers is **`r percentageChange3`%**.

```{r}
#| label: tbl-inquiry1
#| tbl-cap: "Table of inquiries to STEP LC by DMHAS Region"
#| warning: false


#calls the script that makes both the table and runchart
source("Code/02_PSViz_Fig1a1b_inquiryRegionsTable&Runchart.r")
table1
```

```{r, fig.width=5, fig.height=3}
#| label: fig-inquiry2
#| fig-cap: "Inquiries to STEP LC over time & by region"
#| fig-align: center
#| warning: false

#calls the script that makes both the table and runchart
inquiryRunchart
```


## Information about referrers - who made the inquiries?

```{r, fig.width=10, fig.height=5}
#| label: fig-referrersRoutes
#| fig-cap: "Referrals to the LC via clinical and community nodes. This is further split by how these groups heard about the initiative"
#| fig-subcap: 
#|  - "Community referral nodes"
#|  - "Clinical referral nodes"
#|  - "Community referral nodes among eligible people"
#|  - "Clinical referral nodes among eligible people"
#| fig-align: center
#| warning: false
#| layout-ncol: 1

#calls the script that makes both the clinical and community plots
source("Code/02_PSViz_referrersClinical&Community_barchart.r")
plot1
plot2
plot3
plot4

# get summarys stats for text
commMax<-comm_df %>%
    summarise(n=n()) %>%
    filter(n==max(n)) 

clinMax<-clin_df %>%
    summarise(n=n()) %>%
    filter(n==max(n))  

```

Those referred to the LC via a clinical route primarily came via **`r clinMax$Clinical_Referral`** (n = `r clinMax$n`). Whereas for the community node, the **`r commMax$Community_Referral`** route has been the most prevalent (n = `r commMax$n`).

Referrers to the LC program heard about the initiative in various ways (see @fig-referrersRoutes).

## Who was found to be eligible for the Learning Collaborative initiative?

So far, **`r Eligbile_Text$n`** people have been eligible for the LC, and **`r Under18_Text$n`** were aged under 18yrs (see @fig-EligXRegion).

Individuals did not meet LC eligibility criteria for a range of reasons (n=**`r sum(Ineligible_Text$n)`**; see @fig-ineligibility) and were provided with appropriate information on referrals and resources.

Remaining cases are either engaged in further assessment (n=`r PendingActivecases_text$n`), or remain unresolved (n=`r PendingInactivecases_text$n`).

```{r}
#| label: fig-EligXRegion
#| fig-cap: "Capturing eligibility information by region and age"
#| fig-subcap: 
#|  - "Eligibility rates by region"
#|  - "Pie chart showing age of eligible indivdiuals."
#| warning: false
#| layout-ncol: 2

#calls the script that makes the barchart eligible by region, and pie under 18
source("Code/02_PSViz_eligibleXregion_bar&eligibleXage_Pie.r")
eligibleXregion_bar
eligibleUnder18_pie

```

```{r}
#| label: fig-ineligibility
#| fig-cap: "Reasons for ineligibility to the LC"
#| warning: false

#calls the script for the barchat showing reasons for inelgibility
source("Code/02_PSViz_IneligibleReasons_barchart.r")
gg3_bar

```

## Referrals to LMHAs across Connecticut

The **`r Eligbile_Text$n`** eligible individuals have been referred to their local mental health facilities. Of those, **`r number_admitted`** have been successfully admitted (see @tbl-tabLMHArefs_consent_new for wait times by individual care facility). @fig-map is a map of Connecticut. Here, we can see number of eligible cases by zipcode.

```{r}
#| label: tbl-tabLMHArefs_consent_new
#| tbl-cap: "Table showing number average wait time to admission (date of consent to the LC to date of admission to care)."
#| warning: false

#calls the table with wait time from consenting to LC to admission to LMHA
source("Code/02_PSViz_DUPTableLMHAs.r")
DUPTable

```

```{r, fig.width=3.5, fig.height=3.5}
#| warning: false
#| label: fig-map
#| fig-cap: "Heatmap of Connecticut, split by zipcodes, and coloured by number of indivdiuals currently found to be eligible for the LC"

#calls scripts that makes the eligibility map by zipcode
source("Code/03_RCViz_MAP_eligibeXzip.r")
p1_eligibleZips

```

We had **`r number_not_admitted`** case where it can be determined that the individiual will not end up successfully enrolled at the 3 month mark (see @tbl-patients_rejected_referral_table). There are also **`r number_awaiting_admission`** cases where admission with the agency is yet to be confirmed.

```{r, fig.width=3.5, fig.height=3.5}
#| label: tbl-patients_rejected_referral_table
#| tbl-cap: "Table showing number of eligible individuals where the referral did not land, and why"
#| warning: false

#calls script that makes the table showing reasons why patients didnt land
source("Code/02_PSViz_tablePatientsNotAdmitted.r")
tablePatientsNotAdmitted
```

## Demographic and symptom data

The following section provides an overview of individuals found to be eligible for the LC (n=**`r Eligbile_Text$n`**). Here, we provide information regarding the distribution of various baseline datapoints such as age, gender, race, income, and drug use.

```{r}
#| warning: false
#| label: fig-demos
#| fig-subcap: 
#|  - "Age group by gender (%)"
#|  - "Race category membership (%)"
#|  - "Labor statistic employment category (N)"
#|  - "Household and personal income (%)"
#| layout-ncol: 2

source("Code/03_RCViz_demos_4.r")

#calls script that make pyramid plot for age and gender
pyramid_plot

#calls script that makes the barchart for race/ethnicity
gg4

#calls script that makes the BLS employment waffle plot
gg1_new

#calls script that makes barchart for income
incomeplot
```

```{r}
#| warning: false
#| label: fig-drugs
#| fig-cap: "Figure showing drug use as measured by the Alcohol Use and Drug Use scale"

#calls script that makes the drug/alcohol use barchart
source("Code/03_RCViz_DRUGS_barchart.r")
gg2_drugsbar

```

```{r}
#| warning: false
#| label: fig-sympsAndsuicideet
#| fig-subcap: 
#|  - "Lifetime suicide and judicial involvement"

#calls script that makes lifetime suicide and judicial involvement plot
source("Code/03_RCViz_suicideXlegalXviolence_bar.r")
gg2_bar

```
